---
title: "R Markdown Intro"
author: "Rob Wells"
date: "4/30/2019"
output: html_document     
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###Load software packages

```{r load_software, echo=TRUE}
library(tidyverse)
library(rmarkdown)
library(knitr)
library(vembedr)
pacman::p_load(rmarkdown, dplyr, fst, scales, purrr, rio)
```

#The Lowdown on Markdown:    

  --Create web pages, PDFs, presentations, Word documents      
  --Add formatting to plain text    
  --knit the file - include charts, data in the text  
  --Works with knitr package   
  --Examples: Course syllabus, Sabew, IRE Presentations  
  
  *[2018 IRE Presentation](http://bit.do/biz-watchdogs)    
  *[2018 Sabew Presentation](http://bit.do/sabewdata)

###Tutorial    
* [From rStudio](https://rmarkdown.rstudio.com/articles_intro.html)
 
The file demonstrates how to use markdown to indicate:    

    1. *headers* - Place one or more hashtags at the start of a line that will be a header (or sub-header). For example, # Say Hello to markdown. A single hashtag creates a first level header. Two hashtags, ##, creates a second level header, and so on.   
    2. *italicized and bold text* - Surround italicized text with asterisks, like this *without realizing it*. Surround bold text with two asterisks, like this **easy to use**.      3. *lists* - Group lines into bullet points that begin with asterisks. Leave a blank line before the first bullet    
    
###Tutorial
* [Andrew Ba Tran](http://learn.r-journalism.com/en/publishing/)   
    

###Play video from 9:00   
* [Part1](https://www.youtube.com/watch?v=uOh9A1JW_wA)

###Your Turn: Open a new .Rmd file: 

File > New File > R Markdown.
Every .Rmd file starts out the same at the top.

YAML HEADER
Optional section of render options written as key:value pairs.

At start of file
Between lines of — (3 dashes)
This is how R knows how to render your files. 
In the example above, the lineoutput: html_document means it will create an HTML file. If it was output: pdf then you’d get a PDF instead.

You can output more than one type at a time, if you want.

###CODE CHUNKS
In the image above, the R code is in the gray area.
These are chunks of embedded R code. Each chunk:
begins with ```{r} (the back tick key is to the left of 1)
ends with ```

Here is a code chunk. To Run this code, click the green diamond on the below right

```{r cars_chunk}
summary(cars)
```

See how a plot is displayed. To Run this code, click the green diamond on the below right

```{R plot_a_chart}
plot(pressure)
```


##Render a PDF file in RMarkdown    

      Create an R Markdown Document
      Copy a few lines from your R cheat sheet into it

      library(rmarkdown)
      render("/Users/robwells/Dropbox/Classes/Data-Analysis-Class-Jour-405v-5003/CheatSheet2019.Rmd", output_format="pdf_document", output_file = "CheatSheet2019.pdf" )    

##Now, render it as an html page    
 
      render("/Users/robwells/Dropbox/Classes/Data-Analysis-Class-Jour-405v-5003/CheatSheet2019.Rmd", output_format="html_document", output_file = "CheatSheet.html")  
      
##Now host html on GitHub    

     * *[](http://learn.r-journalism.com/en/git/github/github/)

      Hosting with Github Pages  
      Turn http://github.com/username/reponame/index.html ->
      Into http://username.github.io/reponame/index.html

      github.io is the address for hosted files

      First: Set up Github to host the files.
      Setting up GH Pages

      1) After uploading your repo, click on Settings on the top right.

      2) Scroll down to the GitHub Pages section of Settings.

      3) Change the Source from None to master branch and click save.

      For future projects, you can organize your files so that all output HTML are stored        in a docs folder. Then the option master branch\docs will host those files and ignore       everything in the root folder.

      Now go to https://YOURUSERNAME.github.io/YOUR-REPO-NAME/YOUR-FILE-NAME.html and you        should have your hosted file!

      https://profrobwells.github.io/Testrepo/CheatSheet.html

#REVEL IN YOUR NERD POWERS  
#REVEL IN YOUR NERD POWERS  
#REVEL IN YOUR NERD POWERS
